---
title: 'Milestone #3'
author: "Dominic Skinnion"
date: "10/3/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(readxl)
library(tidyverse)
library(fivethirtyeight)
```

```{r election data}
elections <- read.csv("raw-data/elec.csv")
```

```{r population data}
population <- read.csv("raw-data/nhgis0011_ts_state.csv")
```

As of now, I have the election data from the git hub link included above. It is a collection of election data from the earliest elections. I am not sure if I need to move it to my raw-data file or not, since I can download it directly from the web to my RMarkdown file. If I do, please let me know! Georgie found the data set for me from a github repo with links to a bunch of cool political data sets. So far, I have only loaded it in using read.csv.

I also included population data by state found on git-hub, but the years are by decade (I'm guessing because of the census?) when I need the dates to match election years. I think that I should be able to run exponential regressions in order to calculate an estimated population during election years. I have also included the fivethirtyeight library because I anticipate that they will have a vast dataset that will probably be of use to me, although I will need to do further digging to see what possible sets I could use.

I plan on looking at the trend in electoral power by state and how it changes over time. I think it would be cool to see which states have fallen in and out of voting power. I also want to see which states have a disproportionate voting power to population (by dividing electoral votes by population) and seeing how those have changed over time. Georgie and I also discussed looking at how those states tend to vote (e.g. say Montana has a higher proportion of EV:population and it typically votes R, then Republicans would get an advantage). We also discussed looking to see if there were any datasets that had information on the number of eligible and registered voters in states, to see voter turnout, etc., but I have not found any data for earlier elections on that yet. 
